Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-19 checking-executions.tex
modify

The following lemma states the correctness of $\textit{Check-PQ-Seq}$ (the proof can be found in Appendix~\ref{}). {\color {blue}Therefore, in latter section we can abuse $\seqPQ$ by the set obtained by renaming sequences that are accepted by $Check-PQ-Seq$.}

@@

The following lemma states the correctness of $\textit{Check-PQ-Conc}$. Completeness follows easily from the properties of $\seqPQ$. Thus, if $\textit{Check-PQ-Conc}(e) = \textit{false}$, then there exists a set of values $D$ such that one of the following doesn't hold: $\mathsf{EmptyRemove\text{-}Conc}(e \vert D)$, {\color {blue}$\mathsf{UnmatchedMaxPriority\text{-}Conc}(e \vert D,x)$ for some maximal priority values $x$, or $\mathsf{MatchedMaxPriority\text{-}Conc}(e \vert D,x)$ for some maximal priority values $x$.} It can be easily seen that we get $e \vert D\not\sqsubseteq \seqPQ$ in all cases, which by the closure under projection of $\seqPQ$ implies, $e \not\sqsubseteq \seqPQ$ (since every linearization of $e$ includes as a subsequence a linearization of $e \vert D$).

>>>>

The following lemma states the correctness of $\textit{Check-PQ-Seq}$ (the proof can be found in Appendix~\ref{}).

@@

The following lemma states the correctness of $\textit{Check-PQ-Conc}$. Completeness follows easily from the properties of $\seqPQ$. Thus, if $\textit{Check-PQ-Conc}(e) = \textit{false}$, then there exists a set of values $D$ such that one of the following doesn't hold: $\mathsf{EmptyRemove\text{-}Conc}(e \vert D)$, {\color {blue}$\mathsf{UnmatchedMaxPriority\text{-}Conc}(e \vert D,x)$ for all values that are unmatched and with maximal priority $x$, or $\mathsf{MatchedMaxPriority\text{-}Conc}(e \vert D,x)$ for all maximal priority values $x$ where values of $x$ are all matched.} It can be easily seen that we get $e \vert D\not\sqsubseteq \seqPQ$ in all cases, which by the closure under projection of $\seqPQ$ implies, $e \not\sqsubseteq \seqPQ$ (since every linearization of $e$ includes as a subsequence a linearization of $e \vert D$).
